---
title: "README"
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# regista

[![Build Status](https://travis-ci.org/Torvaney/regista.svg?branch=master)](https://travis-ci.org/Torvaney/regista)
[![Coverage status](https://codecov.io/gh/Torvaney/regista/branch/master/graph/badge.svg)](https://codecov.io/github/Torvaney/regista?branch=master)

## Overview

regista is a package for performing some of the common modelling tasks in soccer
analytics. Currently a *work in progress*.

## Installation

regista is not currently available on CRAN but can be downloaded from github like so:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("torvaney/regista")
```

## Examples

### Dixon-Coles

The ["Dixon-Coles model"](http://web.math.ku.dk/~rolf/teaching/thesis/DixonColes.pdf) is a modified poisson model, specifically designed for estimating teams' strengths and for predicting football matches. 

Regista provides an implementation of this model:

```{r, message = FALSE, warning = FALSE}
library(regista)

fit <- dixoncoles(hgoal, agoal, home, away, data = premier_league_2010)

print(fit)
```

The Dixon-Coles model provides estimates of each team's offensive and defensive strength, along with
an estimate of home-field advantage (`hfa`):

```{r}
parameters <- data.frame(parameter = names(fit$par),
                         value     = fit$par,
                         row.names = NULL)

head(parameters)
```

Regista also comes with a `predict` method to predict method, to either predict the goalscoring rate of either team, or the probabilities of different possible scorelines:

```{r}
with_predictions <- cbind(
  premier_league_2010,
  predict(fit, premier_league_2010, type = "rates")
)

head(with_predictions[, c("date", "home", "away", "home_rate", "away_rate")])
```

A more flexible api is provided with `dixoncoles_ext`, which allows the base Dixon-Coles model to be extended arbitrarily.

There are some more extensive examples and analyses using regista available at the following links:

 * [Modelling the World Cup with regista](http://www.statsandsnakeoil.com/2018/06/05/modelling-the-world-cup-with-regista/)
 * [Dixon Coles and xG: together at last](http://www.statsandsnakeoil.com/2018/06/22/dixon-coles-and-xg-together-at-last/)
 * [What a diff'rence xG makes](http://www.statsandsnakeoil.com/2018/07/15/what-a-diff-rence-xg-makes/)
